---
title: "Quadratic Function"
author: "Humphrey"
date: '2022-05-31'
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)

```

A quadratic equation is an equation of the form $ax^2+bx+c=0$, where `a`, `b`, and `c` are constants. One can solve the value of `x` given the values of `a`, `b` and `c` using the quadratic formula below:
$$x=\frac{-b\pm\sqrt{b^2-4ac}}{2a},\qquad where\quad a\neq0 $$
The roots are real and distinct when the discriminant $b^2-4ac$ is equal to zero, real and equal when the discriminant is equal to 0 and complex if the discriminant is less than zero.
The function is:

```{r}
quadratic= function(a,b,c){
  x=(-b+c(-1,1)*(sqrt(b^2-(4*a*c))))/(2*a)
  x
}
```

Lets take for example the equation $x^2-45x+324$. The roots are real and distinct. In this case, `a=1`, `b=-45` and `c=324`. We pass a,b and c as the arguments of the function and the pair of roots is generated.
```{r}
quadratic(a=1,b=-45,c=324)
```
However, this will not work in the case of complex roots. The below function will tell you if the roots are complex.
```{r}
quadratic2 = function(a, b, c){
  discriminant = b^2 - 4*a*c
  x1 = (-b - sqrt(discriminant))/(2*a)
  x2 = (-b + sqrt(discriminant))/(2*a)
  if (discriminant < 0){
    cat("The roots are complex");
     
  }
  else
  
  cat("The two roots are", x1, "and", x2, "\n");
}
```

Click [here](https://github.com/HumphreyKn) to Follow me on Github
